The \project{unRAVE} catalog

### 2016-09-07 article/unrave.tex
De-stubbing

These constraints forced us to construct a heterogeneous training set.  Given previous
successes in transferring high S/N ratio labels from \apogee\ \citep{Ness_2015,
Ness_2016,Ho_2016,Casey_2016b}, we chose to use the 1,355 stars in the \apogee---\rave\ 
overlap sample for giant star labels in the training set.  Of these, about 900 are 
giants according to \apogee.  From this sample we selected stars to have: 
determinations in all abundances of interest ([X/H] $> -5$ for O, Mg, Al, Si, Ca, Fe, and Ni); S/N ratios of $>$200 in \apogee\ and $>$25 in \rave; and 
we further required that \aspcap\ did not report any peculiar flags 
(\texttt{ASPCAPFLAG = 0}).  These restrictions left us with 536 stars along the giant 
branch, with metallicities ranging from $[{\rm Fe/H}] = -1.79$ to 0.26.  Intermediate 
tests with globular cluster members showed that the metallicity range of the training 
set needed to extend below $[{\rm Fe/H}] \lesssim -2$ in order for our catalog to be 
practically useful.  \stub{Supplemented this sample with known metal-poor stars in \rave}.

@@

We sought to have a small overlap between our giant and main-sequence star training
sets.  Most of our giant training set is encapsulated within $0 < \logg < 3.5$, 
however there is a sparse sampling of stars reaching to $\logg \approx 4$.  We
required $\logg > 3.5$ for the \epic\ main-sequence/sub-giant star training set,
allowing for $\approx0.5$~dex of overlap between the two training sets.  We further
employed the following quality constraints: the upper and lower confidence intervals 
in $\teff$ must be below 150~K; the upper and lower confidence intervals in $\logg$ 
must be less than 0.15~dex; the $S/N$ of the \rave\ spectra must exceed 
30~pixel$^{-1}$; and $\teff \leqslant 6750$~K.  Unfortunately these strict constraints
removed most metal-poor stars, which we later found to cause the test labels to have
under-predicted abundances for dwarfs of low metallicity.  For this reason we relaxed
(ignored) those quality constraints for stars with $[{\rm Fe/H}] < -1$.  
\stub{Include known metal-poor stars in \rave?}. After training
a model based on main-sequence and giant stars (Section \ref{sec:the-model}), we found 
we could identify misclassifications by leave-one-out cross-validation.  However, we 
chose not to do this because the number of likely misclassifications in the training
set was negligible ($\approx1$\%), and the improvement in main-sequence test set labels
was minimal.  The distilled sample of the \rave--\epic\ overlap catalog contains 583 
stars (of 4,611).  The full training set for each model (see next sections) is shown
in Figure~\ref{fig:training-set-hrd}.

>>>>

These constraints forced us to construct a heterogeneous training set.  Given previous
successes in transferring high S/N ratio labels from \apogee\ \citep{Ness_2015,
Ness_2016,Ho_2016,Casey_2016b}, we chose to use the 1,355 stars in the \apogee---\rave\ 
overlap sample for giant star labels in the training set.  Of these, about 900 are 
giants according to \apogee.  From this sample we selected stars to have: 
determinations in all abundances of interest ([X/H] $> -5$ for O, Mg, Al, Si, Ca, Fe, and Ni); S/N ratios of $>$200 in \apogee\ and $>$25 in \rave; and 
we further required that \aspcap\ did not report any peculiar flags 
(\texttt{ASPCAPFLAG = 0}).  These restrictions left us with 536 stars along the giant 
branch, with metallicities ranging from $[{\rm Fe/H}] = -1.79$ to 0.26.  Intermediate 
tests with globular cluster members showed that the metallicity range of the training 
set needed to extend at least below $[{\rm Fe/H}] \lesssim -2$ in order for our catalog 
to be practically useful.  Without additional metal-poor stars, the lowest metallicity
labels reported by our model would be around $[{\rm Fe/H}] \approx -2$, even for well
studied stars with $[{\rm Fe/H}] \sim -4$ (e.g., CD~38-245).  For this reason we
supplemented our sample of \apogee\ giant stars with 176 known metal-poor giant stars 
observed by \rave.  The effective temperature $\teff$, surface gravity $\logg$ and
iron abundance [Fe/H] labels were adopted from \citet{Fulbright_2010, Ruchti_2011}.
The elemental abundances for O, Mg, Al, Si, Ca, and Ni were assumed to follow typical
trends of Galactic chemical evolution, such that we assumed $[{\rm Mg/Fe}] = +0.4$,
$[{\rm O/Fe}] = +0.4$, $[{\rm Al/Fe}] = -0.5$, $[{\rm Ca/Fe}] = +0.4$, 
$[{\rm Si/Fe}] = +0.4$, and $[{\rm Ni/Fe}] = -0.25$.  This decision is made solely 
to ensure that our overall metallicity scale extends that of the \rave\ survey, down 
to $[{\rm Fe/H}] \sim -4$.  In other words, we do not recommend the use of individual 
abundance labels at $[{\rm Fe/H}] \sim -4$; in practice the abundances of most of these
elements are largely unrecoverable in the \rave\ wavelength region at $[{\rm Fe/H}] \sim -4$.
We discuss this issue in more detail in Section~\ref{sec:discussion}.

@@

We sought to have a small overlap between our giant and main-sequence star training
sets.  Most of our giant training set is encapsulated within $0 < \logg < 3.5$, 
however there is a sparse sampling of stars reaching to $\logg \approx 4$.  We
required $\logg > 3.5$ for the \epic\ main-sequence/sub-giant star training set,
allowing for $\approx0.5$~dex of overlap between the two training sets.  We further
employed the following quality constraints: the upper and lower confidence intervals 
in $\teff$ must be below 150~K; the upper and lower confidence intervals in $\logg$ 
must be less than 0.15~dex; the $S/N$ of the \rave\ spectra must exceed 
30~pixel$^{-1}$; and $\teff \leqslant 6750$~K.  Unfortunately these strict constraints
removed most metal-poor stars, which we later found to cause the test labels to have
under-predicted abundances for dwarfs of low metallicity.  For this reason we relaxed
(ignored) those quality constraints for stars with $[{\rm Fe/H}] < -1$, and included
an additional 12 turn-off stars with $-1.6 \gtrsim [{\rm Fe/H}] \gtrsim -2.1$ from 
\citet{Ruchti_2011}.  After training
a model based on main-sequence and giant stars (Section \ref{sec:the-model}), we found 
we could identify misclassifications by leave-one-out cross-validation.  However, we 
chose not to do this because the number of likely misclassifications in the training
set was negligible ($\approx1$\%), and the improvement in main-sequence test set labels
was minimal.  The distilled sample of the \rave--\epic\ overlap catalog contains 595 
stars (583 of 4,611 from \epic).  The full training set for each model (see next sections) is shown
in Figure~\ref{fig:training-set-hrd}.
